Deploy

### 2021-05-23 deploy_gh.Rmd
Adding deploy features, fix #23

In oolong 0.3.22, functions for deploying oolong tests were added (`export_oolong`, `revert_oolong` etc.). These functions make it possible for the coders to conduct validation tests online using their browser, rather than having to install R on their computer.

@@

<img src="figures/deploying_shinyappsio.png" align="center" height="400" />

@@

<img src="figures/oolong_download.png" align="center"/>

>>>>

---
title: "Deploy"
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/vignettes/figures/README-",
  out.width = "100%"
  )
set.seed(42)
```
In oolong 0.3.22, functions for deploying oolong tests were added (`export_oolong`, `revert_oolong` etc.). These functions make it possible for the coders to conduct validation tests online using their browser, rather than having to install R on their computer.

@@

<img src="vignettes/figures/deploying_shinyappsio.png" align="center" height="400" />

@@

<img src="vignettes/figures/oolong_download.png" align="center"/>
